---
title: "Job Accessibility Regression Analysis"
author: "Transit Equity Team"
date: '2022-06-13'
output:
  pdf_document: default
  html_document: default
---

# Loading data

```{r libraries, message=FALSE}
library(tidyverse)
library(modelr)
library(gt)
```

We begin by loading all of the job accessibility data computed at various thresholds (i.e., what is someone's job accessibility when they're willing to travel via transit (with or without the Red Line) for the stated length of time?).

```{r}
seg <- "SE01"
speed <- "25"
```


```{r find-directories}
#setwd('set your directory to /TransitEquity/')
data_dir <- str_glue("../processed_data/job_accessibility_{seg}_{speed}")
transit_dir <- str_glue("{data_dir}/transit_current")
transit_files <- list.files(transit_dir, pattern = "*.csv")
red_line_dir <- str_glue("{data_dir}/red_line")
red_line_files <- list.files(red_line_dir, pattern = "*.csv")

transit_threshes <- transit_files %>% 
  map_chr(str_remove_all, ".csv") %>% 
  map_dbl(as.double) %>% 
  sort() %>% 
  as_factor()

red_line_threshes <- red_line_files %>% 
  map_chr(str_remove_all, ".csv") %>% 
  map_dbl(as.double) %>% 
  sort() %>% 
  as_factor()
```

```{r load-job-accessibilities}
load_ja <- function(thresh, mode, dir) {
  # This will load a list of job accessibilities from the given directory dir 
  # with the threshold thresh. These values will be tagged with the given 
  # threshold, and mode of transportation.
  read_csv(str_glue("{dir}/{thresh}.csv"), show_col_types = FALSE) %>%
    transmute(FIPS = tract_id, mode = mode,
              threshold = thresh, gravity_sum = gravity)
}

# Load all of the job accessibilities in transit_dir, red_line_dir
transit <- transit_threshes %>%
  map(load_ja, mode = "transit", dir = transit_dir)
red_line <- red_line_threshes %>%
  map(load_ja, mode = "red_line", dir = red_line_dir)

# Join (matching by FIPS) them all into one data frame
all_ja <- bind_rows(transit, red_line) %>% 
  mutate(mode = factor(mode, c("transit", "red_line")))

# Compute the change
all_ja <- all_ja %>% 
  pivot_wider(names_from = mode, values_from = gravity_sum) %>% 
  mutate(difference = red_line - transit,
         pct_difference = difference / transit) %>% 
  pivot_longer(c("transit", "red_line", "difference", "pct_difference"), 
               names_to = "mode", values_to = "gravity_sum")
```

These tracts are in the red-line service area (i.e., 15 minute walk from a red line stop). In future analyses we will filter by these FIPS codes.

```{r}
service_area <- c("24510280404",
"24510280402",
"24510160500",
"24510280401",
"24510160802",
"24510160801",
"24510200701",
"24510200702",
"24510160700",
"24510160600",
"24510200200",
"24510160400",
"24510160300",
"24510200400",
"24510200100",
"24510160200",
"24510190200",
"24510160100",
"24510190100",
"24510170300",
"24510280600",
"24510180300",
"24510280600",
"24510170100",
"24510040200",
"24510040100",
"24510260501",
"24510030200",
"24510020100",
"24510020300",
"24510260800",
"24510260700",
"24510010200",
"24510030100",
"24510020200",
"24510010500",
"24510260900",
"24510010300",
"24510261100",
"24510220100",
"24510010100")

all_ja <- all_ja %>% mutate(service_area = FIPS %in% service_area)
```

Now we will join the job accessibility with the computed socioeconomic index. This is computed by summing all socioeconomic SVI indicators except for percentage of uninsured persons. We also tag those FIPS that have below-mean indices.

```{r load-svi}
svi <- read_csv("../processed_data/SVI_EP_2020_Standard_Scaled_Summary_Index.csv", 
    col_types = cols_only(FIPS = "d", 
      svi_socioecon_summary = "d")) %>% 
    mutate(disadvantaged = svi_socioecon_summary < 0)
svi_ja <- svi %>% left_join(all_ja, by = "FIPS")
```

# Plot results

We first show the change in job accessibility at different thresholds.

```{r job-accessibility-plots}
ggplot(data = svi_ja %>% filter(threshold == 45, mode %in% c("red_line", "transit"), service_area == TRUE), mapping = aes(svi_socioecon_summary, gravity_sum)) +
  geom_point(alpha = 0.4) +
  geom_smooth(method = "lm", formula = "y ~ x") +
  facet_grid(mode ~ threshold)
```
```{r job-accessibility-plots}
ggplot(data = svi_ja %>% filter(mode == "pct_difference"), mapping = aes(svi_socioecon_summary, gravity_sum)) +
  geom_point(alpha = 0.4) +
  geom_smooth(method = "lm", formula = "y ~ x") +
  facet_grid(mode ~ threshold)
```

```{r}
ggplot(data = svi_ja, mapping = aes(gravity_sum)) +
  geom_histogram()+
  facet_grid(mode ~ threshold)
```
```{r}

```


```{r}
svi_ja %>% filter(mode %in% c("transit", "red_line"), service_area == TRUE, threshold == 60) %>%
  ggplot(mapping = aes(x = mode, y = gravity_sum)) +
  geom_boxplot() +
  facet_grid(. ~ disadvantaged)
```

```{r}
ggplot(data = svi_ja %>% filter(threshold == 45, mode %in% c("difference")), mapping = aes(x = gravity_sum)) +
  geom_boxplot()
```
```{r}
svi_ja %>% filter(threshold == 45, mode %in% c("difference"), gravity_sum > 20) 
```

We can also compare our SVI indicator against average travel times.

```{r load-average-travel-time}
transit_time <- read_csv(str_glue("../processed_data/transit_time_data_speed_{speed}.csv"), show_col_types = FALSE)
job_flows <- read_csv(str_glue("../processed_data/job_flow_tract_{seg}.csv"), 
                      show_col_types = FALSE)

transit_time <- transit_time %>%
  left_join(job_flows, 
            by = c("origin" = "h_geocode", 
                   "dest" = "w_geocode")) %>% 
  mutate(job_totals = replace_na(job_totals, 0))

transit_time <- transit_time %>% 
group_by(origin) %>% 
  mutate(
    flow_proportion = job_totals / sum(job_totals)) %>%
  summarize(
    transit = sum(transit_time_current * flow_proportion),
    red_line = sum(transit_time_with_red_line * flow_proportion)) %>%
  mutate(difference = red_line - transit,
         pct_difference = difference / transit) %>% 
  pivot_longer(c("transit", "red_line", "difference", "pct_difference"),
               names_to = "mode", 
               values_to = "average_transit_time")
svi_transit_time <- svi %>%
  inner_join(transit_time, by = c("FIPS" = "origin")) %>% 
  mutate(service_area = FIPS %in% service_area)
```

```{r transit-time-plots}
ggplot(data = svi_transit_time %>% filter(service_area == TRUE, mode %in% c("red_line", "transit")), 
     mapping = aes(svi_socioecon_summary, average_transit_time)) +
  geom_point(alpha = 0.4) +
geom_smooth(method = "lm", formula = "y ~ x") +
  facet_grid(. ~ mode)
```
```{r transit-time-plots}
ggplot(data = svi_transit_time %>% filter(mode %in% c("difference")), 
     mapping = aes(svi_socioecon_summary, average_transit_time)) +
  geom_point(alpha = 0.4) +
geom_smooth(method = "lm", formula = "y ~ x") +
  facet_grid(. ~ mode)
```

```{r}
ggplot(data = svi_transit_time %>% filter(mode %in% c("pct_difference"), service_area == TRUE), 
       mapping = aes(x = disadvantaged, y = average_transit_time)) +
  geom_boxplot() 
# +
# facet_grid(service_area ~ .)
```