---
title: "Understanding Clusters"
author: "Transit Equity Team"
date: '2022-06-14'
output: html_document
---

Load clustered SVI data. This is the same as the raw SVI data with each census tract given a cluster label. The two clusters were computed using the indices loading onto the first factor in the factor analysis, followed by projection via UMAP and clustering via spectral clustering.

```{r load-data, message=FALSE}
#setwd('set your directory to /TransitEquity/')
library(tidyverse)
svi_clustered <- read_csv("processed_data/SVI_E_clustered.csv", 
    col_types = cols(FIPS = col_skip(), cluster = col_factor(levels = c("0", 
        "1"))))
```


Visualize the densities of each indicator separately on the two clusters.

```{r visualise-density}
svi_means <- svi_clustered %>% 
  group_by(cluster) %>% 
  summarize_all(mean)

for(col in colnames(svi_clustered)){
  if(grepl('E', col, fixed = TRUE)){
    column = svi_clustered[[col]]
    g1 <- ggplot(data=svi_clustered, aes_string(x=col, fill='cluster')) +
               geom_density(alpha=.3) +
               geom_vline(mapping = aes_string(xintercept=col, color='cluster'), data = svi_means, show.legend = FALSE) +
               labs(title = "Density plot with cluster means", x=col)
    print(g1)
  }
}
```

Visualize the boxplots of each indicator separately on the two clusters.

```{r visualise-boxplots}
for(col in colnames(svi_clustered)){
  if(grepl('E', col, fixed = TRUE)){
    column = svi_clustered[[col]]
    g1 <- ggplot(data=svi_clustered, aes_string(x=col, fill="cluster")) +
               facet_grid(rows=vars(cluster)) +
               geom_boxplot(alpha=.3) + labs(x=col)
    print(g1)
  }
}
```

Note that the cluster labeled "0" is considered more socially vulnerable by most every index.